Hydras \& Co.

### 2022-02-02 doc/gaia-chapter.tex
minor changes

@@

Please note that in this module, we favour \gaia's notations over hydra's. A snippet like \texttt{alpha < succ beta} should be interpreted as \texttt{T1lt alpha beta}, where \texttt{T1lt} is defined in \texttt{gaia.ssete9.v}. The corresponding statement is
written \texttt{hlt (g2h alpha) (g2h beta)}.

@@

The following lemmas are proved by rewriting from corresponding statements proved in \Hydras.

>>>>

From now on, names like  \texttt{T1}, \texttt{omega}, etc. are  bound to \Hydras's meaning.

 \inputsnippets{ T1Bridge_use/LocateT1, T1Bridge_use/T1BridgeUseb}

@@

Please note that in this module, we favour \gaia's notations over hydra's. A snippet like \texttt{alpha < succ beta} should be interpreted as \texttt{T1lt alpha beta}, where \texttt{T1lt} is defined in ~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}.

\texttt{gaia.ssete9.v}. The corresponding statement is
written \texttt{hlt (g2h alpha) (g2h beta)}.

@@

The following lemmas are proved by rewriting from corresponding statements proved in \Hydras.
\emph{The author of these proof scripts is still a beginner in Ssreflect. Please forgive the clumsiness of the scripts below.}
